%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Chronosphere} % Organization
{Member of Technical Staff} % Job title
{Remote} % Location
{Nov. 2023 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Rapid Response Team building observability features to get customers signed}
    \item {Bulit observability features responsible for 10s of million dollars in revenue}
    \item {GCP Monitoring Integration / Metrics Ingestion Pipeline}
    \item {Alert Rule Evaluation}
    \item {Public/Internal API (GRPC/HTTP/GraphQL)}
    \item {SLO / Monitoring}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Fullstory} % Organization
{Senior Site Reliability Engineer} % Job title
{Remote} % Location
{Feb. 2021 - Nov. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Infrastructure Security Compliance / Customer Checklist Audit and Implementation}
    \item {GCP IAM permission management service, permission audit, OSLogin, workload identity}
    \item {Metrics / Compute Scaling and Cluster Migration / Upgrade}
    \item {Migrate to infrastructure-as-a-code through Terraform / Atlantis / Ansible}
    \item {Custom CI/CD solution for Kubernetes and Compute instances}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Compose, an IBM Company} % Organization
    {Platform Engineer} % Job title
    {Remote} % Location
    {Jan. 2017 - Feb 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database-as-a-Service orchestration engine for Compose / IBM Cloud Database (PostgreSQL, MongoDB, ElasticSearch, RabbitMQ and more)}
        \item {Database administration automation (provision, backup, scaling, resync, recovery etc.)}
        \item {Go microservices, Kubernetes operators, CRD, Jobs to manage database replicas}
        \item {Monitoring infrastructure through kube-prometheus (prometheus and grafana), ELK, Sensu}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Republic of Korea Cyber Command} % Organization  
    {Sergeant, Software Engineering} % Job title
    {Seoul, S.Korea} % Location
    {Feb. 2015 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cybersecurity web services}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advanced Micro Devices Inc.} % Organization  
    {ASIC Design Engineer 2} % Job title  
    {Markham, Canada} % Location
    {Aug. 2013 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {PCIe post-silicon debugging}
        \item {PCS IP (PCIe, USB, SATA) design verification}
        \item {C++, Perl, System Verilog, Verilog, UVM}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Aversan Inc.} % Organization  
    {Software Engineer (Java)} % Job title  
    {Mississauga, Canada} % Location
    {Nov. 2012 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Custom reverse proxy and test automation framework for eHealth Ontario}
        \item {Java, Netty, Spring, Hibernate, Maven, Oracle 11g, Selenium}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advanced Micro Devices Inc.} % Organization  
    {ASIC Design Engineer (PEY)} % Job title  
    {Markham, Canada} % Location
    {May. 2010 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {DFx IP (DFT/DFD) design verification}
        \item {IEEE standards (JTAG, P1500)}
        \item {C++, Perl, System Verilog, Verilog}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\vspace{14mm}
